Online {\IterComp}

### 2017-11-14 motivation.tex
adds corr_coeff fig for all benchmarks
updates speedup and adds figures

    \paragraph{Iterative compilation needs representative inputs.} 
    In order to highlight what happens when we apply iterative compilation using the wrong set of inputs, we selected two distinct sets of
    10 out of the 1,000 inputs of the of \textit{KDataSets}~\cite{chen10,chen12a} for the \texttt{tiff2bw} benchmark.
    The first set represents the training set, i.e., the set of inputs that will be used for selecting the best optimization sequence by
    iterative compilation, and the second set is a specific set of inputs which is misrepresented by the training set.
    After performing iterative compilation on the first set, the selected optimization sequence has an average speedup of 1.22 over -O3 for
    the training set itself, but it produces a slowdown of 0.91 for the second set of inputs.
    However, if the iterative compilation was performed on the second set itself, it would be able to find a optimization sequence that
    produces a speedup of \FIXME{1.02} over -O3.

@@

>>>>

    \paragraph{Iterative compilation needs representative inputs.} 
    In order to highlight what happens when we apply iterative compilation using the wrong set of inputs, we selected two distinct sets of
    10 out of the 1,000 inputs of the of \textit{KDataSets}~\cite{chen10,chen12a} for the \texttt{tiff2bw} benchmark.
    The first set represents the training set, i.e., the set of inputs that will be used for selecting the best optimization sequence by
    iterative compilation, and the second set is a specific set of inputs which is misrepresented by the training set.
    After performing iterative compilation on the first set, the selected optimization sequence has an average speedup of 1.22 over -O3 for
    the training set itself, but it produces a slowdown of 0.91 for the second set of inputs.
    However, if the iterative compilation was performed on the second set itself, it would be able to find a optimization sequence that
    produces a speedup of 1.07 over -O3.

\begin{figure}[t]
    \centering
    \includegraphics[width=0.7\linewidth]{figs/motivation_wrong_inputs.pdf}
    \caption{Iterative compilation performed on the wrong set of inputs compared to the ideal case for the \texttt{tiff2bw} benchmark.}
    \label{fig:motivation_wrong_inputs}
\end{figure}

@@

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figs/corr_coeff.pdf}
    \caption{Correlation coefficient.}
    \label{fig:corr_coeff}
\end{figure*}

### 2017-11-14 work.tex
updates speedup and adds figures

    To build a reasonable work metric, our approach starts by assuming that each executed instruction\footnote{In this paper, we consider instructions at the level of the intermediate representation of the LLVM compiler.} contributes a certain amount towards
    the total useful work. To keep the measurement simple and minimize the online overhead, we assume that the contribution depends only on
    the type of instruction. Additionally, we would expect two program versions processing the same data in the same way to do the same
    work. If measured using the actual instructions executed for the two versions, we would get a different amount of work. Instead, we
    increase the total work based on the instructions that would be executed with the unoptimized code, regardless of the version we use.
    The unoptimized version is convenient as a common baseline, since we start with it anyway and it is as close as possible to the
    programmer's intention.

>>>>

    To build a reasonable work metric, our approach starts by assuming that each executed instruction\footnote{In this paper, we consider instructions at the level of the Intermediate Representation (IR) of the LLVM compiler.} contributes a certain amount towards
    the total useful work. To keep the measurement simple and minimize the online overhead, we assume that the contribution depends only on
    the type of instruction. Additionally, we would expect two program versions processing the same data in the same way to do the same
    work. If measured using the actual instructions executed for the two versions, we would get a different amount of work. Instead, we
    increase the total work based on the instructions that would be executed with the unoptimized code, regardless of the version we use.
    The unoptimized version is convenient as a common baseline, since we start with it anyway and it is as close as possible to the
    programmer's intention.
